Historical Soil Organic Carbon Budget

### 2020-05-19 SOCbudgetPaper/methods.Rmd
Update methods.Rmd

Following the tier 2 approach of the refinement of IPCC guidelines vol. 4 (@ipcc_2019_2019), we estimate global land-use type specific soil organic carbon (SOC) stocks for cropland and natural vegetation on half-degree resolution from 1965 to 2010. We assume the actual SOC state converges towards a stable steady state, that itself is changing over time and space depending on biophysical, climatic and agronomic conditions. Therefor we conduct the following three steps: 
(1) Calculating annual land-use (sub-)type specific steady states and decay rates for SOC stocks, 
(2) accounting for land conversion by transferring SOC between land-use types and 
(3) updating SOC stocks based on the previous stock, the steady state and the decay rate.

@@

>>>>

Following the tier 2 approach of the refinement of IPCC guidelines vol. 4 (@ipcc_2019_2019), we estimate global land-use type specific soil organic carbon (SOC) stocks for cropland and natural vegetation on half-degree resolution from 1965 to 2010. We assume the actual SOC state converges towards a stable steady state, that itself is changing over time and space depending on biophysical, climatic and agronomic conditions. Therefore we conduct the following three steps within each yearly timestep: 
(1) We calculate annual land-use (sub-)type specific steady states and decay rates for SOC stocks, 
(2) We account for land conversion by transferring SOC between land-use types and 
(3) We estimate SOC stocks based on the stocks of the previous time period, the steady state stocks and the decay rate.

@@

This equation can also be reformulated to a massbalance equation as follows:

\begin{equation}
SOC_{t} = SOC_{t-1} (1 - k_{t} \cdot 1\unit{a}) + C^{\textrm{in}}  \qquad \forall lut, sub, i.
\label{eq:steadystate}
\end{equation}
